intro

### 2022-01-28 06_Paper/ER-ED/TheoreticalBackground.Rmd
added figure 1

library(targets)    # to keep track of all relevant files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs.
### Hier sollte auch noch erwähnt werden, dass wir auch n-back erheben

## 1.2 The present study

>>>>

library(targets)    # to keep track of all relevant files
library(knitr)
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
### Hier sollte auch noch erwähnt werden, dass wir auch n-back erheben
```{r fig1, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
```
## 1.2 The present study
